Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-20 Report06-12.Rmd
figures directory reference

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){
    img <- image_read(paste0("images/", i))

>>>>

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){
    img <- image_read(paste0("figures/", i))
